Certified Desugaring of Javascript Programs using Coq

### 2016-12-13 paper/paper.tex
additional notes on what to say
Added reference to the ADsafe paper.
Converted to biblatex and biber.

\usepackage{natbib}

@@

\usepackage{todonotes}
\newcommand{\as}[1]{\todo[color=green]{#1}}
\newcommand{\asi}[1]{\todo[color=green,inline]{#1}}

@@

\begin{itemize}
\item give figures on test coverage
\item say we created tests for bugs
\end{itemize}

@@

One such semantics is \lambdajs. It aims to capture
the semantics of JavaScript by defining a simple core language
(based on the untyped call-by-value lambda calculus), and then
transforming (or ``desugaring'') the full JavaScript language into this
simple core. The \lambdajs semantics was originally developed to model the 
ECMAScript 3 specification~\citep{Guha-al:ECOOP10}, and it was later
revised~\citep{Politz-al:DLS12} to handle ECMAScript 5.1
features.\footnote{The authors named the revised language S5; however,
we continue to name it \lambdajs for simplicity.}
The interpreter for the core language and the JavaScript-to-core
transformation were developed using 
OCaml;\footnote{\url{https://github.com/brownplt/LambdaS5}}
the interpreter was tested using the official test262 test suite.
The \lambdajs semantics is useful for tool developers, as it
allows the tools to analyze JavaScript programs by working
on the simple core language of \lambdajs, having all the complexities
of JavaScript handled in the desugared code. It was already
successfully used to verify AdSafe. \as{add citation}

More recently, JSCert~\citep{Bodin-al:POPL14},
formalized the ECMAScript 5.1 specification in the form of
a pretty-big-step semantics~\citep{Chargueraud:ESOP13} expressed in 
the form of a Coq inductive predicate. It aims to be as close to the
(informal English) specification as possible by maintaining close correspondence
between the evaluation rules and steps in the ES5 pseudocode. The project
also includes JSRef, a reference interpreter for JavaScript written in Coq
and proven correct with respect to JSCert. The interpreter is also tested
using the official ECMA test suite, test262. Thanks to the correctness proof,
testing of JSRef increases the confidence we can have that JSCert
correctly models ES5.

@@

To reduce the complexity of the task, we are currently working
only on proving \lambdajs correct with respect to JSCert,
i.e., that if the \lambdajs program successfully terminates,
then its result matches the result given by JSCert. We are also
restricting our attention to ECMAScript strict mode, proving the
correctness of non-strict features only when it is convenient.
\asi{How difficult would it be to prove the other direction (if we have a
  derivation in JSCert, then we have one in \lambdajs?)}

@@

At this stage we stumbled upon an interesting performance issue 
involving the Coq proof assistant. The proof of completeness required
inverting the pretty-big-step semantics judgment; this turned out
to be very slow, and also generated large proof terms, which increased
the memory footprint. The problem is well-known~\citep{Monin:Coq2}; 
our solution involved
precomputing the required inversion principles using
\texttt{Derive Inversion}, and using the precomputed inversion
principles to create a specialized inversion tactic.

@@

\bibliographystyle{plain}

\bibliography{mybib}

>>>>

\usepackage[backend=biber,bibencoding=utf8]{biblatex}

\addbibresource{mybib.bib}

@@

\usepackage{todonotes}
\newcommand{\as}[1]{\todo[color=green]{#1}}
\newcommand{\asi}[1]{\todo[color=green,inline]{#1}}
\newcommand{\mm}[1]{\todo[color=blue]{#1}}
\newcommand{\mmi}[1]{\todo[color=blue,inline]{#1}}

@@

\begin{itemize}
\item give figures on test coverage
\item say we created tests for bugs
\item say thanks to Valentin Lorentz, to the people at Brown
\item related work: KJS
\end{itemize}

@@

One such semantics is \lambdajs. It aims to capture
the semantics of JavaScript by defining a simple core language
(based on the untyped call-by-value lambda calculus), and then
transforming (or ``desugaring'') the full JavaScript language into this
simple core. The \lambdajs semantics was originally developed to model the 
ECMAScript 3 specification~\cite{Guha-al:ECOOP10}, and it was later
revised~\cite{Politz-al:DLS12} to handle ECMAScript 5.1
features.\footnote{The authors named the revised language S5; however,
we continue to name it \lambdajs for simplicity.}
The interpreter for the core language and the JavaScript-to-core
transformation were developed using 
OCaml;\footnote{\url{https://github.com/brownplt/LambdaS5}}
the interpreter was tested using the official test262 test suite.
The \lambdajs semantics is useful for tool developers, as it
allows the tools to analyze JavaScript programs by working
on the simple core language of \lambdajs, having all the complexities
of JavaScript handled in the desugared code. It was already
successfully used to verify ADsafe~\cite{Politz-al:SEC11}.

More recently, JSCert~\cite{Bodin-al:POPL14},
formalized the ECMAScript 5.1 specification in the form of
a pretty-big-step semantics~\cite{Chargueraud:ESOP13} expressed in 
the form of a Coq inductive predicate. It aims to be as close to the
(informal English) specification as possible by maintaining close correspondence
between the evaluation rules and steps in the ES5 pseudocode. The project
also includes JSRef, a reference interpreter for JavaScript written in Coq
and proven correct with respect to JSCert. The interpreter is also tested
using the official ECMA test suite, test262. Thanks to the correctness proof,
testing of JSRef increases the confidence we can have that JSCert
correctly models ES5.

@@

To reduce the complexity of the task, we are currently working
only on proving \lambdajs correct with respect to JSCert,
i.e., that if the \lambdajs program successfully terminates,
then its result matches the result given by JSCert. We are also
restricting our attention to ECMAScript strict mode, proving the
correctness of non-strict features only when it is convenient.
\asi{How difficult would it be to prove the other direction (if we have a
  derivation in JSCert, then we have one in \lambdajs?)}
\mmi{It would require inverting the JSCert semantic judgments.
  Is this working now? I remember Petar trying to do this.}

@@

At this stage we stumbled upon an interesting performance issue 
involving the Coq proof assistant. The proof of completeness required
inverting the pretty-big-step semantics judgment; this turned out
to be very slow, and also generated large proof terms, which increased
the memory footprint. The problem is well-known~\cite{Monin:Coq2}; 
our solution involved
precomputing the required inversion principles using
\texttt{Derive Inversion}, and using the precomputed inversion
principles to create a specialized inversion tactic.

@@

\printbibliography
